Trump vs. Harris: A 2024 US Presidential Elections Modelling Forecast

### 2024-11-06 paper/paper.qmd
Updated paper

---
title: "Trump vs. Harris: A 2024 US Presidential Elections Modelling Forecast"
subtitle: "Trump trumps Harris to become the next President of the United States"
author: 
  - Sophia Brothers
  - Deyi Kong
  - Rayan Awad Alim
thanks: "Code and data are available at: [https://github.com/eeeee-cmd/US_Election/](https://github.com/eeeee-cmd/US_Election/)."
date: today
date-format: long
abstract: "This paper predicts the 2024 U.S. Presidential election. We utilizes linear regression model deploying polling data and demographic factors to predict both popular vote and Electoral College outcomes. The findings indicate a close race between Donald Trump and Kamala Harris, and we predict Trump will secure the Electoral College and Popular Vote due to key wins in tight races for the Battleground States. The results emphasize the role of state-level dynamics, particularly in Battleground states, in determining election outcomes."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Trump vs. Harris: A 2024 US Presidential Elections Modelling Forecast"
subtitle: "Trump trumps Harris to become the next President of the United States"
author: 
  - Sophia Brothers
  - Deyi Kong
  - Rayan Awad Alim
thanks: "Code and data are available at: [https://github.com/eeeee-cmd/US_Election/](https://github.com/eeeee-cmd/US_Election/)."
date: November 4, 2024
date-format: long
abstract: "This paper predicts the 2024 U.S. Presidential election. We utilizes linear regression model deploying polling data and demographic factors to predict both popular vote and Electoral College outcomes. The findings indicate a close race between Donald Trump and Kamala Harris, and we predict Trump will secure the Electoral College and Popular Vote due to key wins in tight races for the Battleground States. The results emphasize the role of state-level dynamics, particularly in Battleground states, in determining election outcomes."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---
